The Freeplay Sandbox: a Novel Methodology for the Evaluation of Social Robotics

### 2017-10-05 paper.tex
Reworked the abstract

We introduce in this paper a novel interaction situation designed for ecological
validity while ensuring `good' scientific properties (replicable, clear metrics,
possibility of both autonomous and Wizard-of-Oz robot behaviours).
This task focuses on child-robot interaction in a \emph{sandboxed} free-play
environment. We present hereafter the rationale for this task, its technical and
practical aspects (including the open-source source code), as well as two
large datasets that represent interaction baselines for this task.

>>>>

Evaluating in a rigorous manner human-robot social interactions is notoriously
difficult~\cite{baxter2016characterising}: studies are either conducted in labs
with constrained protocols to allow for robust measurements and a degree of
replicability, but at the cost of ecological validity; or \emph{in the wild},
which leads to superior experimental realism, but often with limited
replicability and at the expense of rigorous interaction metrics.

We introduce in this paper a novel interaction paradigm, designed to elicit rich
and varied social interactions while exhibiting `good' scientific properties
(replicable, clear metrics, possibility of either autonomous or Wizard-of-Oz
robot behaviours). This paradigm focuses on child-robot interactions, and
builds on a sandboxed free-play environment. We present hereafter the
rationale and design of this interaction paradigm, its associated
methodological and technical aspects (including the open-source
implementation of the software platform), as well as two large open datasets
acquired with this paradigm, and meant to act as experimental baselines for
future research.
